\thesistitle

### 2019-07-19 sections/conclusion.tex
TODO everywhere

\subsection{Refactoring the harder to refactor clones}
In section \ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction. Because we strived to get results fast, we excluded catagories that could not not be directly refactored through method extraction. However, with a few transformations or further considerations it might be possible to make these clones refactorable.

@@

\subsection{Running our experiments with a greater diversity of software projects}
Currently

\subsection{Automatically refactoring code that is duplicated with a library}

>>>>

\subsection{Refactoring the harder to refactor clones}
In section \ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction. Because we strived to get results fast, we excluded categories that could not not be directly refactored through method extraction. However, with a few transformations or further considerations it might be possible to make these clones refactorable. In this section we will highlight a few of these categories which we believe to be refactorable through method extraction with a bit more effort.

\subsubsection{Partial method}
\todo{TODO}

\subsubsection{Overlap}
\todo{TODO}

\subsubsection{Complex control flow}
\todo{TODO}

@@

\subsection{Running our experiments with a greater diversity of software projects}
\todo{TODO}

\subsection{Automatically refactoring code that is duplicated with a library}
\todo{TODO}
